The limits of self commitment and private paternalism \thanks{}

### 2020-08-14 main.tex
appendix B and updates in paper

@@

\title{Private paternalism and the limits of self commitment  \thanks{We want to thank Craig McIntosh and Mauricio Romero for advice and encouragement. We want to thank also Ricardo Olivares for excellent research assistance and Erick Molina help with formatting. Jose Maria Barrero, Emilio Gutierrez, Aprajit Mahajan, Matt Rabin, and seminar participants at ITAM provided very valuable feedback.}}
\author{Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx;  
Seira: ITAM, enrique.seira@itam.mx} }
\date{This draft:  \today \\[2 cm]}

@@

\maketitle
\begin{abstract}

@@

We study the benefits of ``private paternalism'' in the understudied but important pawnbroker context. We show that forcing people into commitment contracts with financial penalties for not paying on time \textit{decreases} their (fee-including) financial cost by 9.5\%, increases the likelihood of recovering their pawn by 25\%, and increases the likelihood of repeat business by 55\%. Using the recent machine learning methods for estimating heterogeneous treatment effects, we calculate that more than 90\% clients would reduce their financing cost with the commitment contract, however 10\% choose it. Using personal promises instead of fees as commitment triples take-of but has no effects.

@@

\textbf{Keywords: } Private paternalism, choice, present bias, naivete, overconfidence, commitment, pawnshop.

@@

@@

\cite{Laibson2018} recently noted that many institutions ---firms, schools, financial contracts--- restrict choice using built-in incentive/commitment mechanisms which help workers, students, borrowers overcome self-control problems. ``Firms do limit their workers' freedom with intermediate deadlines, progress reports, production targets'', schools with ``pop quizzes, classroom attendance requirements, cold calling, graded problem sets, deadlines''. Similarly, mortgages do so ``with a fixed repayment stream and mandatory principal repayment''. However he notes that these same firms shroud these forcing mechanisms and don't market their commitment features, presumably because students, workers and borrowers ``don't welcome these paternalistic\footnote{\cite{Laibson2018} defines paternalism as a policy that advances an individual's interests by restricting his or her freedom, and private paternalism as paternalism implemented by private institutions.} restrictions''. In this he sees an important \textit{commitment puzzle}: if clients were present biased and  sophisticated about their self control problem they should appreciate commitment features and firms should be eager to market them. The fact that this is not the case suggests some clients may be naive about their self control problems, and that \textit{private paternalism}  ---a policy of restricting choice implemented by private firms--- may increase clients' welfare.

This paper studies private paternalism in the context of pawnbroker borrowing and finds evidence for its benefits. Pawnshops offer secure loans using items of personal property as collateral. The items pawned are called pledges or pawns. Pawn loans are one of the oldest forms of borrowing, and although data on their market share is scarce, anecdotal evidence suggests they are very prevalent. To give an example, our partner pawnshop (henceforth Lender $P$) served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were approximately 2.3 million micro-finance clients in Mexico in 2009 in Mexico (\cite{Pedroza:2010}). We cannot be more precise on the number of total borrowers from Lender $P$ for confidentiality reasons.}  Pawn loans are interesting to study in and on themselves for this reason alone. But they are also interesting because regulators and practitioners view pawnbrokers as the lenders to which people in desperate need turn to. The regulators' concern is that the selection of clients that go to pawnshops may be particularly vulnerable, have bad debt management skills, and be more likely to have present biased preferences while being naive about it.\footnote{In 2013 Mexico's Consumer Protection Bureau (Profeco) is concerned about abuse. It forced Pawnshops to be more transparent in their pricing, register their contracts with them and issued regulation to protect clients. Congress has enacted laws in this regard. \url{http://www.diputados.gob.mx/LeyesBiblio/ref/lfpc.htm}.}

Indeed, using a survey conducted by us in branches of Lender $P$, we document some evidence consistent with regulators' concerns: while pawnshop clients predict they will recover their pawn with 93\% probability on average, in reality only 40\% of them do, suggesting naivete. Even conditional on paying a positive amount towards pawn recovery, 53\% lose their pawn and their payment. In our survey 69\% report self-control problems saying they often fall into temptation spending. %, but only \hlgr{15\%} show inter-temporal inconsistencies in a classical present-bias question, a similar number to \cite{Ashaf}. %and \hl{19\%} do not normally budget monthly expenses. 
%While this is suggestive of a present bias problem or overconfidence to save and pay, at the same time our subjects are experienced and not wholly uneducated, 66\% have completed at least high school and 90\% have pawned before. %and \hl{38\%} have participated in a Rosca.

Consistent with little client sophistication, Lender $P$ offers a very simple but highly collateralized contract. It only accepted gold jewelry as collateral and approves all gold pawns, giving in exchange in cash the equivalent of 70\% of the weighted gold value. The contract stipulates a 7\% monthly interest rate charged daily, and a loan term of 90 days plus 15 grace days to pay the principal and the accumulated interest. The client has complete flexibility to pay any number of times any amount she desires towards the recovery of her pawn, with no pre-payment penalties. However if the total amount of principal plus interest is not covered by the end of the 105 days, she loses her pawn and all the payments that have been done (unless she renews the loan before this by paying all accumulated interest). All transactions ---appraisal of the piece, loan disbursement and loan servicing--- are conducted at the branch. The gold collateral is highly liquid and the pawnshop has an associated business that sells the gold jewelry. Given the over-collateralization of the loan one would expect no moral hazard or adverse selection on the part of borrowers. %This lets us focus more cleanly on behavioral economics aspects.

To study the benefits of private paternalism, we implemented a relatively large randomized control trial with close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City. We answer five main questions using this experiment. First, would clients benefit  ---in terms of recovering their pawn and in terms of incurring in lower financing costs---  from having a frequent (monthly) payment commitment contract \textit{forced} on them, instead of the current 3-month pay-when-you-want contract? That is, we are asking whether \textit{charging} them a 2\% late payment fee for not paying a monthly installment on time can actually \textit{decrease} total fee-inclusive financing cost. Second, would there be demand for such a frequent payment commitment contract vis-a-vis the status quo one if given choice? Notice that any payment profile implemented in the commitment contract can be replicated by the borrower under the status quo contract, but the later affords more flexibility to respond to income shocks without incurring in fees. Third, what types of clients would demand these contracts that restrict choice? Fourth, are late payment fees key to provide commitment or would a non-pecuniary but salient personal promise to pay provide a cost-reducing mix of commitment vs flexibility? A large and important lab experiment literature suggest that promises change behavior significantly in laboratory settings, but we know little about their effect on the field in natural environments.\footnote{Some important papers in this space are \cite{PromisesPartnerships}, \cite{Vanberg}, \cite{Belot2010}, \cite{WhyDoPromises}, \cite{FurtherPromises}, \cite{Ismayilov2017}. There is also some actual policy around using promises for loans: the government Mexico has created a program called ``Loans on your word'' for uncollateralized borrowing (\url{http://tiny.cc/yfmnmz}). There is little information about them though.} Finally and importantly, is \textit{giving choice} among contracts better than forcing them into payment-commitment contracts in terms of minimizing financing costs incurred and the likelihood of recovering their pawn? Or on the contrary, is it better to force the commitment contract 
paternalistically?

The experiment involved 5 arms, with randomization happening at the branch-day level. It is described in detail in Section \ref{Experiment}. Here let us briefly explain the main 3 arms. The first one involves a group of clients that were given only the status quo contract (henceforth the \textit{status-quo forcing group}). The second arm (\textit{fee-forcing group}) was given only a monthly payment commitment contract, which stipulated that clients had to pay 1/3 of their loan plus accumulated interest in each of the 3 months of the term length. Failing to do this would result in a fee of 2\% of the amount due that month. A third group (\textit{Fee-choice group}) gave clients a choice between these two contracts.

We find that forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more. The effects are large: financing cost decreases by 9.5\% on average, while the likelihood of recovering their pawn increases by 25\%. Results are robust to including in the cost definition transport costs of going to the branch plus losing a day's wage for each visit. Importantly, the benefits are distributed broadly: the whole distribution of treatment effects shows cost savings. The most economically vulnerable, those that report being stressed, and those that asked for a reminder at baseline, experience the largest financial cost savings. Those we classify as present biased and those that requested a reminder at baseline experience the largest effects on pawn recovery. %The commitment contract also causes payments to start 8 days earlier and be 16\% more frequent, compared to the control group. 
Treatment effects are concentrated on the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. It seems that the fee-commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost. Finally, we find that borrowers assigned to the forced fee-commitment contract are 5pp (55\% of the mean) more likely to be repeat costumers than the control group, suggesting that they themselves liked the commitment contract more after experiencing it.

@@

In spite of these estimated benefits for all clients, their actual demand for the fee-commitment contract is low. Only 10\% of the group offered a choice between the monthly payment fee-commitment contract and the status-quo one chose the former. This is not likely driven by misunderstanding the (already simple) contract.\footnote{We had two ITAM students in each of the experiment's branches every day for all branch opening hours to carefully explain the contracts; material was developed to explain the differences among the two contracts, and subjects spelled back to our ITAM assistants the loan differences. Furthermore take up is systematically predicted by baseline covariates, %\footnote{We find that the more educated, those that report that their family typically asks for money, those that make a monthly budget of expenses, and ask for a remainder to payment (and marginally those we classify as present-biased) are more likely to chose the fee-commitment contract if given the choice. The opposite holds for those that are more vulnerable (can barely pay for food, electricity, etc) and those that report being more stressed.}, 
making it less likely that it is just random mistakes.} Low demand for commitment is consistent with a large part of the literature of the literature (\cite{Laibson2015}, \cite{Laibson2018}, \cite{John}, \cite{Ted}, \cite{Rabin2018}).%\footnote{\cite{Alcohol} and \cite{Kremer} are some of the few instances of high demand for commitment. \cite{Alcohol} speculates that this difference may be explained by their subjects having more experience with their self control problem. Close to ninety percent of our subjects claim to have pawned before. We find that experience does not predict positive take up in our sample.} 
\cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can severely limit take-up when agents are naive about their self control, even though commitment could be welfare improving for them. We estimate zero average treatment effects of the \textit{fee-choice} arm on financial cost and on pawn recovery and throughout the quantile distribution.

@@

How much money is left on the table by the prevalence of the status-quo choice? We calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost. On average they spend an extra \$238 pesos, close to 11\% of the average loan value. In particular 92\% of those that chose the status-quo contract would have been better in the fee-commitment contract, while only 8\% of those who chose the fee-commitment contract would have been better in the status-quo one. This suggests that forcing clients into commitment contacts (i.e. private paternalism) may be welfare increasing for the overwhelming majority of clients.

Inspired by a significant lab experiment literature on the effects of promises on behavior, we also implemented a ``psychological commitment'' in the form of a salient promise to pay.  \cite{PromisesPartnerships}, \cite{FurtherPromises}, \cite{Vanberg}, and \cite{Ismayilov2017} find that the ability to make a promise about behaving a certain way makes the individual more likely to adhere to the promised behavior. %and also induces trusting behavior by the recipients of the promise. 
To do this we implemented two other treatment arms. A \textit{promise-forcing} arm exactly analogous to our \textit{fee-forcing arm} except that instead of telling them that there is a fee if they don't pay on time, we made borrowers promise that they would pay one third of the amount in each of the 3 months, and told them that if they didn't they would have broken their promise and failed their word. Because salience is key we made them sign a (non-legally binding) personal promise and emphasized we were counting on them to keep their promise. A final arm (\textit{promise-choice arm}) gave clients the opportunity to choose between the \textit{Promise-forced} contract and the \textit{Status-quo} contract.

We document two main results in the promise arms. First, demand for the commitment-promise contract is three times bigger than for the commitment fee contract, with 31\% take-up. This difference between both choice arms suggests that clients are indeed understanding and taking into account the contractual parameters in their choice, and that the fee commitment was probably too strong from their point of view. Second, the \textit{Promise-forcing} contract had zero effects on average and throughout the distribution on financing cost and pawn recovery. The same is true for the \textit{Promise-choice arm}. %\footnote{There is a decrease in financial cost in the 50th and 75th quantiles in the forced promise-commitment arm however.}
Promises did not provide enough commitment so as to be reflected in behavior. This is true both imposed promises and chosen promises. Contrary to lab evidence, people did not keep the promise, at least the way it could be implemented in the field.

We contribute to several strands of literature. First, to the broad literature on commitment demand. A significant literature has shown that demand for commitment exists but is somewhat low in some contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}), and high in others (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}). We add to this literature by showing that very small fees are enough to drastically reduce demand for commitment, even when commitment is beneficial for almost everybody in our sample, and that softer commitments in the form of non-pecuniary personal promises elicit higher demand.\footnote{Our fees are 16 times smaller than than those of \cite{John} as a fraction of the loan/goal, and five times smaller converting peso values using exchange rates.} Second, two recent papers show that among those who demand commitment, the extent of commitment needed is underestimated (\cite{Ted}, \cite{John}) and that subjects can hurt themselves by self-imposing too week a commitment. We contribute in design ---by not allowing choice of the extent of commitment--- but also on how we infer the underestimation of the value of commitment by subjects. While these two papers infer too low commitment from subjects failing to reach the goal ex-post, we infer it by quantifying forgone personalized treatment effects ex-ante. Third, we focus on an important new context: pawnshop borrowing. Pawnshop borrowing is extremely prevalent in developing countries and very worrisome to regulators, yet severely understudied.

Fourth, we study \textit{both} causal effects and selection into frequent payment commitment loan contracts. \cite{Ghatak} state that ``high-frequency repayment, a feature in nearly all microfinance contracts, has been largely overlooked''.\footnote{\cite{LittleAtAtime} also note that ``it is especially surprising that there is so little analytical discussion of the incentive effects of the installment system''.} This paper fills part of this gap. \cite{Pande} study the effect of installment payment frequency on loan default and (surprisingly given their prevalence and the literature above) find null effects. \cite{Murdoch} study selection into frequent payment microfinance loans, conjecturing that ``such repayment structure is potentially beneficial in fostering discipline among present-biased borrowers'' and may explain why borrowers choose it. In contrast to \cite{Pande} we find strong effects of payment frequency on decreased default.\footnote{Possibly because there are high levels of default in our context and not in theirs and because we have more statistical power from a larger sample and individual level randomization.} \cite{Murdoch}  show that a robust positive correlation exists between displaying present biased preferences in surveys and selecting into microfinance ---which they interpret as being due to high demand for the discipline of frequent payments--- acknowledging that the ``interpretation is suggestive... and needs to be confirmed by studies that establish causal links''. Our experimental test of this causal link rejects that most people like and demand frequent payments (at least in our context). In contrast to \cite{Murdoch} we can isolate the pure effect of payment frequency on demand by randomly changing just this aspect of the contract. Fifth, we also contribute to the literature on the effect of promises by testing their effect on the field.

More importantly, our unique experimental design which combines forcing and choice arms, paired with new machine learning methods to estimate heterogeneous treatment effects (\cite{atheygrf}), allows us to estimate whether there is positive or negative selection into beneficial contracts, and whether pawnshop clients forgo money by not demanding commitment. In consonance with what \cite{Walters} finds in another context, we find that it is not the case that those that benefit most from the contract demand it more, consistent with a significant fraction of clients displaying naivete about self control problems (see \cite{Rabin2018}). Our context is one in which private paternalism (\cite{Laibson2018}) could work since almost all pawnshop clients would benefit from frequent payment contract yet there it almost no demand for them. After our experiment ended, Lender P started to tie in installment payment components to some of their contracts themselves.

@@

This contract was standard in the industry, the clients that pawned understood its conditions (as we verified in interviews) and still decided to pawn.\footnote{90\% of clients report in our survey they have pawned before.} Bear in mind that these clients have little or no access to other types of loans, and also that they value its convenience: the process is fast and requires no documentation or credit-history. Potentially they like it also because they are overconfident on average about the probability of recovering their pawn, as discussed below.

@@

\subsection{More on implementation.} \label{implementation}

>>>>

%para esconder columnas en tablas (enrique)
\usepackage{array}
\newcolumntype{H}{>{\setbox0=\hbox\bgroup}c<{\egroup}@{}}

@@

\title{The limits of self-commitment and private paternalism \thanks{We want to thank Craig McIntosh and Mauricio Romero for advice and encouragement. We want to thank also Ricardo Olivares for excellent research assistance and Erick Molina's help with formatting. Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM provided valuable feedback.}}
\author{Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx;  
Seira: ITAM, enrique.seira@gmail.com} }
\date{This draft:  \today \\[2 cm]}

@@

\maketitle
\thispagestyle{empty}
\begin{abstract}

@@

In the context of pawnbroker lending, we show that forcing people into commitment contracts with financial penalties for not paying on time \textit{decreases} their (fee-including) financial cost by 9.5\%, increases the likelihood of recovering their pawn by 25\%, and increases the likelihood of repeat business by 55\%. Using machine learning methods for estimating heterogeneous treatment effects, we find that more than 90\% clients would reduce their financing cost with the commitment contract, however only 10\% choose it. Relying on personal promises instead of fees as commitment triples take-up but has no effects on outcomes.

@@

\vspace{.3in}

\textbf{Keywords: } Private paternalism, choice, present bias, naivete, overconfidence, commitment, heterogeneous treatment effects.

@@

\pagenumbering{arabic}

@@

Many institutions ---firms, schools, financial contracts--- restrict choice using built-in commitment mechanisms which help workers, students, borrowers overcome self-control problems. For instance, mortgages restrict choice ``with a fixed repayment stream and mandatory principal repayment \citep{Laibson2018}''.\footnote{\cite{Laibson2018} also mentions that ``Firms do limit their workers' freedom with intermediate deadlines, progress reports, production targets'', and schools with ``pop quizzes, classroom attendance requirements, cold calling, graded problem sets, deadlines''.} At the same time  these same firms shroud these forcing mechanisms and don't market their commitment features, presumably because students, workers and borrowers ``don't welcome these paternalistic restrictions'' (\cite{Laibson2018}). \cite{Laibson2018} argues that this presents an important commitment puzzle: if clients were present biased and sophisticated about their self control problem they should appreciate commitment features and firms should be eager to market them. That this is not so suggests some clients may be naive about their self control problems, and that private paternalism may be beneficial.\footnote{\cite{Laibson2018} defines paternalism as a policy that advances an individual's interests by restricting his or her freedom, and private paternalism as paternalism implemented by private institutions. In this paper we will study the effect of restricting freedom of choice on pawn recovery and financing cost, not overall welfare.}

This paper studies the benefits of restricting choice in the context of pawnbroker lending. Pawn loans are one of the oldest, understudied, and most prevalent forms of borrowing. There are more than 11,000 pawn shops across the US with 30 million clients and \$14 billion yearly revenues (in China is a 43 billion industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).} The key characteristic of pawn loans is that the borrower leaves personal property (a pawn) as collateral in exchange of an immediate cash loan of a smaller value. In our case Lender $P$ only accepts gold jewelry as collateral and approves all pawns, giving cash the equivalent of 70\% of the pawn's appraised value. The contract stipulates a 7\% monthly interest rate charged daily, a loan term of 90 days, and the flexibility to pay back the loan at anytime before the loan is due. In spite of this flexibility, most people lose their pawn, and among those that recover it almost all of them pay in the last days, just before the loan elapses.\footnote{In the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).}

% About 85\% of borrower lose their pawn\footnote{https://nationalpawnbrokers.org/2017/06/19/pawnbroking-around-the-world/}

%different prices: https://priceonomics.com/the-economics-of-pawn-shops/

% pawnshops help the poor https://tinyurl.com/y9qr43j8
%, with annual percentage rates above or close to 200\%.

% Limite statustics and knowledge of pawnshops. World bank mentions them in passing: https://tinyurl.com/ydgob8pv

%Borrowers typically turn to these loans when in desperate need to pay for an emergency. The vulnerability of these borrowers has sparked regulator's interest.\footnote{In 2013 Mexico's Consumer Protection Bureau (Profeco) is concerned about abuse. It forced Pawnshops to be more transparent in their pricing, register their contracts with them and issued regulation to protect clients. Congress has enacted laws in this regard. \url{http://www.diputados.gob.mx/LeyesBiblio/ref/lfpc.htm}.} One concern is that borrowers selecting into these loans may exhibit particularly strong behavioral biases. 
%Using a survey conducted by us in branches of Lender $P$, we indeed document some evidence consistent with these concerns: while pawnshop clients predict they will recover their pawn with 93\% probability on average, in reality only 40\% of them do, suggesting naivete. 
%Even conditional on paying a positive amount towards pawn recovery, 53\% lose their pawn and their payment. In our survey 69\% report self-control problems saying they often fall into temptation spending. %, but only \hlgr{15\%} show inter-temporal inconsistencies in a classical present-bias question, a similar number to \cite{Ashaf}. %and \hl{19\%} do not normally budget monthly expenses. 
%While this is suggestive of a present bias problem or overconfidence to save and pay, at the same time our subjects are experienced and not wholly uneducated, 66\% have completed at least high school and 90\% have pawned before. %and \hl{38\%} have participated in a Rosca.

\begin{comment}
Lender $P$ offers a very simple but highly collateralized contract. It only accepts gold jewelry as collateral and approves all gold pawns, giving in cash the equivalent of 70\% of the weighted gold value. The contract stipulates a 7\% monthly interest rate charged daily, and a loan term of 90 days plus 15 grace days to pay the principal and the accumulated interest. The client has complete flexibility to pay any number of times any amount she desires towards the recovery of her pawn, with no pre-payment penalties. However if the total amount of principal plus interest is not covered by the end of the 105 days, she loses her pawn and all the payments that have been done (unless she renews the loan before this by paying all accumulated interest). All transactions ---appraisal of the piece, loan disbursement and loan servicing--- are conducted at the branch. The gold collateral is highly liquid and the pawnshop has an associated business that sells the gold jewelry. Given the over-collateralization of the loan one would expect no moral hazard or adverse selection on the part of borrowers. %This lets us focus more cleanly on behavioral economics aspects.
\end{comment}

We implemented a large randomized control trial with close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City. We answer five main questions using this experiment. First, would clients benefit  ---in terms of recovering their pawn and in terms of incurring in lower financing costs---  from having a frequent (monthly) payment commitment contract \textit{forced} on them, instead of the current 3-month pay-when-you-want contract? That is, we are asking whether \textit{charging} them a 2\% late payment fee for not paying a monthly installment on time can actually \textit{decrease} total (fee-inclusive) financing cost. Second, would there be demand for such a frequent payment commitment contract vis-a-vis the status quo one if given choice? Any payment profile implemented in the commitment contract can be replicated by the borrower under the status quo contract, but the later affords more flexibility to respond to income shocks without incurring in fees. Third, what types of clients would demand these contracts that restrict choice? Fourth, are late payment fees key to provide commitment or would a non-pecuniary but salient personal promise to pay provide a cost-reducing mix of commitment vs flexibility? Promises change behavior significantly in laboratory settings, but we know little about their effect in natural environments.\footnote{Some papers in this space are \cite{PromisesPartnerships}, \cite{Vanberg}, \cite{Belot2010}, \cite{WhyDoPromises}, \cite{FurtherPromises}, \cite{Ismayilov2017}. There is also some actual policy around using promises for loans: the government Mexico has created a program called ``Loans on your word'' for uncollateralized borrowing (\url{http://tiny.cc/yfmnmz}), but unfortunately there is little information about them.} Finally, is \textit{giving choice} among contracts better than forcing them into payment-commitment contracts in terms of minimizing financing costs incurred and the likelihood of recovering their pawn? Or on the contrary, is it better to force the commitment contract 
paternalistically?

The experiment involved 5 arms, with randomization happening at the branch-day level. It is described in detail in Section \ref{Experiment}. Here let us briefly explain the main 3 arms. The first one involves a group of clients that were given only the status quo contract (henceforth the \textit{status-quo forcing group}). The second arm (\textit{fee-forcing group}) was given a monthly payment commitment contract, which stipulated that clients had to pay 1/3 of their loan plus accumulated interest in each of the 3 months of the term length. Failing to do this would result in a fee of 2\% of the amount due that month. A third group (\textit{Fee-choice group}) gave clients a choice between these two contracts.

Forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more. The effects are large: financing cost decreases by 9.5\% on average, from \$3161 to \$2857 MXN, while the likelihood of recovering their pawn increases by 25\%, from 43\% to 54\%. Results are robust to including transport costs of going to the branch plus losing a day's wage for each visit. Importantly, the benefits are distributed broadly: almost the whole distribution of treatment effects shows cost savings; however those most economically vulnerable, those that report being stressed, and those we classify as overconfident experience larger gains. %The commitment contract also causes payments to start 8 days earlier and be 16\% more frequent, compared to the control group. 
Treatment effects are concentrated on the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. The fee-commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost. Finally, borrowers assigned to the forced fee-commitment contract are 5 percentage points (55\% of the mean) more likely than the control group to ask for another loan in the future, suggesting that they liked the commitment contract more after experiencing it.

@@

In spite of these estimated benefits for almost all clients, actual demand for the fee-commitment contract is low. Only 10\% of the group offered a choice between the monthly payment fee-commitment contract and the status-quo one chose the former. This is not likely driven by misunderstanding the (already simple) contract.\footnote{We posted two persons in each of the experiment's branches every day for all branch opening hours to carefully explain the contracts; material was developed to explain the differences among the two contracts, and subjects spelled back to our team the loan differences. Furthermore take up is systematically predicted by baseline covariates, making it less likely that it is just random mistakes.} Low demand for commitment is consistent with a large literature (\cite{Laibson2015}, \cite{Laibson2018}, \cite{John}, \cite{Ted}, \cite{Rabin2018}). 
%\footnote{\cite{Alcohol} and \cite{Kremer} are some of the few instances of high demand for commitment. \cite{Alcohol} speculates that this difference may be explained by their subjects having more experience with their self control problem. Close to ninety percent of our subjects claim to have pawned before. We find that experience does not predict positive take up in our sample.} 
%\cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can severely limit take-up when agents are naive about their self control, even though commitment could be welfare improving for them. 
Owing to this low take-up, we estimate zero average treatment effects of the \textit{fee-choice} arm on financial cost and on pawn recovery and throughout the quantile distribution.

@@

Combining the forcing and the choice arms ---a unique feature of our experiment--- allows us to estimate the counterfactuals to answer the following question how much money is left on the table by the prevalence of the status-quo choice? We calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost. On average they spend an extra \$238 MXN, close to 11\% of the average loan value. In particular 92\% of those that chose the status-quo contract would have been better in the fee-commitment contract, while only 8\% of those who chose the fee-commitment contract would have been better in the status-quo one. This suggests that forcing clients into commitment contacts (i.e. private paternalism) may be beneficial for the overwhelming majority of clients. After seeing our results Lender $P$ introduced frequent payment contracts in their loans portfolio.

We want to clarify that in the paper we are using the word ``paternalism'' in a restricted sense, meaning only that a large majority of clients would incur in lower financial costs from being forced into commitment contracts instead of letting them chose. We are not making claims about overall welfare which is a slippery concept once we accept the possibility of biased beliefs and preferences.

Inspired by a significant lab experiment literature on the effects of promises on behavior, and by research showing that a small fee could drastically reduce demand for commitment of naive present-biased borrowers (\cite{Laibson2015}), we implemented a ``psychological commitment'' in the form of a salient promise to pay.  \cite{PromisesPartnerships}, \cite{FurtherPromises}, \cite{Vanberg}, and \cite{Ismayilov2017} find that the ability to make a promise about behaving a certain way makes the individual more likely to adhere to the promised behavior. %and also induces trusting behavior by the recipients of the promise. 
To measure the causal effect of promises we implemented two other treatment arms. A \textit{promise-forcing} arm exactly analogous to our \textit{fee-forcing arm} except that instead of telling them that there is a fee if they don't pay on time, we made borrowers promise that they would pay one third of the amount in each of the 3 months, and told them that if they didn't they would have broken their promise and failed their word. Because salience is key we made them sign a (non-legally binding) personal promise and emphasized we were counting on them to keep their promise. A final arm (\textit{promise-choice arm}) gave clients the opportunity to choose between the \textit{Promise} contract and the \textit{Status-quo} contract.

We document two main results in the promise arms. First, demand for the commitment-promise contract is three times bigger than for the commitment fee contract, with 31\% take-up. This difference between both choice arms suggests that clients are indeed understanding and taking into account the contractual parameters in their choice, and that the fee commitment was probably too strong from their point of view. In spite of this much higher take-up, the \textit{Promise-choice arm} had no effect on outcomes on average, or even for those who selected into promising. Second, being forced in to the \textit{Promise} contract also had zero effects on average and throughout the distribution on financing cost and pawn recovery. %\footnote{There is a decrease in financial cost in the 50th and 75th quantiles in the forced promise-commitment arm however.}
Promises did not provide enough commitment so as to be reflected in behavior.

This paper contributes to several strands of literature. First, to the broad literature on commitment demand. A significant literature has shown that demand for commitment exists but is somewhat low in some contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}), and high in others (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}). We add to this literature by showing that very small fees are enough to drastically reduce demand for commitment, even when commitment is beneficial, and that softer commitments in the form of non-pecuniary personal promises elicit higher demand.\footnote{Our fees are 16 times smaller than than those of \cite{John} as a fraction of the loan/goal, and five times smaller converting peso values using exchange rates.} Second, \cite{Ted} and \cite{John} show the extent of commitment needed is underestimated even among those that buy it, and that subjects hurt themselves by self-imposing too weak a commitment in the intensive margin. We contribute in design by not allowing choice of the extent of commitment, and methodologically by inferring subjects underestimation of the value of commitment ex-ante from forgone treatment savings, instead of from subjects failing to reach their goal ex-post. Third, we focus on an important new context: pawnshop borrowing. Pawnshop borrowing is extremely prevalent in developing countries and very worrisome to regulators, yet severely understudied.\footnote{The World Bank's CGAP recognizes the importance of pawnshop borrowing worldwide but provides no statistics or analysis on it: \url{https://tinyurl.com/ydgob8pv}.}

Fourth, we study \textit{both} causal effects and selection into frequent payment commitment loan contracts. \cite{Ghatak} state that ``high-frequency repayment, a feature in nearly all microfinance contracts, has been largely overlooked''. %\footnote{\cite{LittleAtAtime} also note that ``it is especially surprising that there is so little analytical discussion of the incentive effects of the installment system''.} 
This paper fills part of this gap. Studying causal effects of installment payment frequency \cite{Pande} find null effects loan default, a surprising result given the prevalence of frequent payment contracts. In contrast  we find strong effects of payment frequency on decreased default.\footnote{There are many differences in context between the papers which may explain the different result. \cite{Pande} focus on group lending with very little default to start with (less than 1\%), while in our case almost half of loans end in default. We also have a larger sample and we focus on individualized loans, which may afford us stronger statistical power to detect effects.} Our result is consistent with \cite{Field} who show that delaying payment in microfinance loans increases default.\footnote{\cite{Craig} use the discipline of regular loan repayments in microfinance to remind people to save and make a savings plan, and find large increases in savings.} On the other hand, studying selection into frequent payment microfinance loans, \cite{Murdoch} conjecture that ``[frequent installment payment] structure is potentially beneficial in fostering discipline among present-biased borrowers'' and may explain why borrowers choose it.  They show that a robust positive correlation exists between displaying present biased preferences in surveys and selecting into microfinance, which they interpret as being due to high demand for the discipline imposed by frequent payments. However they acknowledge that this ``interpretation is suggestive... and needs to be confirmed by studies that establish causal links''. Our experimental \textit{is} a test of this causal link. We can isolate the pure effect of payment frequency on demand by randomly changing just this aspect of the contract. Our experimental results reject the hypothesis that microfinance (pawnshop) clients like and demand frequent payments, at least in our context. Importantly, our unique experimental design which simultaneously combines forcing and choice arms, paired with new machine learning methods to estimate heterogeneous treatment effects (\cite{atheygrf}), allows us to estimate whether there is positive or negative selection into beneficial contracts, and whether pawnshop clients forgo money by not demanding commitment. In consonance with what \cite{Walters} finds in another context, we find that it is not the case that those that benefit most from the contract demand it more. \cite{Sprenger} find a result that is similar to ours: that people how most need commitment (in our case the overconfident who show the greatest financial cost savings) are less likely to demand it. In contrast to \cite{Sprenger}, our context allows us to focus on money savings instead of estimated utility to proxy for benefits of commitment, a narrower but simpler measure. This allows us to measure effects on cost outcomes beyond take up and behavior. Our larger sample allow us to estimate heterogeneous treatment effects non-parametrically and perform counterfactuals this way. Finally, as in \cite{Rabin2018} we are able to contrasts subjects predictions of their behavior with their actual behavior, and how these map to outcomes, but we do it in a natural setting.

Fifth, we also contribute to the literature on the effect of promises by testing their effect on the field. In consonance to this literature we find that people are willing and indeed voluntarily choose to make promises. In contrast to lab evidence however measured behavior was unchanged by promising and people did not keep their promise.\footnote{This is of course not a refutation of this literature. %not least because the laboratory literature is implemented on more tightly controlled environments and focused on subtler aspects of promising, like their effects on second order beliefs and guilt aversion. The context is also different since 
The lab literature has focused mostly on very concrete investment games between two players and looked at the effects of promises on trust and cooperation in those games. However our results do provide a first piece of evidence on the limitations of using promises to change behavior in the field.}

%, consistent with a significant fraction of clients displaying naivete about self control problems (see \cite{Rabin2018}). Our context is one in which private paternalism (\cite{Laibson2018}) could work since almost all pawnshop clients would benefit from frequent payment contract yet there it almost no demand for them. After our experiment ended, Lender P started to tie in installment payment components to some of their contracts themselves.

@@

This contract was standard in the industry, but other lenders also had contracts involving frequent installment payments. The clients that pawned understood its conditions (as we verified in interviews) and still decided to pawn.\footnote{90\% of clients report in our survey they have pawned before.} These clients have little or no access to other types of loans and value the convenience of pawn borrowing. Potentially borrowers like it also because they are overconfident about the probability of recovering their pawn, as discussed below.

@@

\subsection{More on implementation} \label{implementation}
